---
title: "vad_surg_14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the *rmarkdown* document for LVAD and noncardiac surgery for 2014. *SAS* used to identify lvad supported patients during the year.
The dataframe contains only lvad supported patients now. We will need to merge hospital and other files with this to obtain the large dataframe for analysis.

```{r get the libraries into the document}

library(tidyverse);library(survey);library(srvyr);library(mosaic);
library(MASS);library(haven)

```

Get the *SAS* 2014 core file for analysis and tidydata.

```{r read SAS file}

c2014 <- read_sas("D:/LVAD_noncardiac_surgery/lvad14_c.sas7bdat")

# convert var names to lowercase as is usual

names(c2014) <- tolower(names(c2014))

glimpse(c2014)
```

Use the *prccs* columns to identify patients who are having surgical procedures during this admission and which procedures they have. From the *prccs1* and *prccs2* codes seperate surgical procedures into major groups according to body type and type of surgery.

```{r count for pr1 & pr2}
# prccs 1 procedures

pr1_list <- c2014  %>% count(pr1) %>% tbl_df()

pr1_list <- pr1_list %>% arrange(desc(n))


# prccs2 procedures
pr2_list <- c2014 %>% count(pr2)


pr2_list <- pr2_list %>% arrange(desc(n))


pr1_list

pr2_list
```




99.04 = transfusion of RBC
45.13 = endoscopy of small intestine
38.97 = CVP catheter placement with US guidance
45.23 = colonoscopy
88.72 = ECHO
37.64 = removal of LVAD/likely for transplant
38.93 = venous catheterization
89.64 = PA wedge monitoring
93.83 = PT/OT consult
39.95 = hemodialysis
37.21 = RHC procedure
96.04 = endotracheal tube insertion
38.91 = arterial catheterization

```{r diagoses for admission}

dx1 <- c2014 %>% count(dx1)

dx1 %>% arrange(desc(n))

```
Primary diagnosis:

428.23 = acute on chronic heart failure
996.61 = infection due to implant / device implant
v45.89 = prior surgery
427.1 = paroxysmal SVT / fast AF
578.1 = blood stool / PR bleeding
578.9 = GI bleed
537.83 = Angiodysplasia of the stomach/duodenum
790.92 = abnormal coagulation profile
996.72 = embolism due to cardiac device/graft
569.85 = Angiodysplasia of the intestine
584.9 = kidney failure
428.0 = congestive heart failure
428.22 = chronic CHF
428.43 = acute on chronic CHF
425.4 = primary cardiomyopathy
414.8 = IHD
996.09 = mechanical device malfunction/LVAD malfunction
285.1 = Anemia
784.7 = Epistaxis
285.9 = Anemia (unspecified)
431 = intracerebral hemorrage
434.11 = cerebral embolism with infarct
038.9 = unspecified septicemia
434.91 = cerebral A occlusion with cerebral infarct
780.2 = syncope and collapse
790.7 = bacteremia
276.51 = dehydration
486 = pneumonia
862.6 = cellulitis/abcess of skin likely drive-line infection
404.91 = chronic kidney disease
435.9 = cerebral ischemia

```{r infection}
inf <- as.character(c('0380',
'0381', '03810', '03811', '03812', '03819',          
'03842',                  
'03840', '03841', '03843', '03844', '03849',          
'0031', '0202', '0223', '0362', '0382', '0383', '0545',      
'0388',' 0389', '449', '77181', '7907', '99591', '99592',      
'0200', '0208', '0209', '0218', '0219', '0228', '0229', '0230', '0231', '0232',
'0233', '0238', '0239', '024', '025', '0260', '0269', '0270', '0271', '0272',
'0278', '0279', '0300', '0301', '0302', '0303', '0308', '0309', '0312', '0318',
'0319', '03289', '0329', '0330', '0331', '0338', '0339', '0341', '0363', '03681',
'03689', '0369', '037', '0392', '0393', '0394', '0398', '0399', '0400', '0401',
'0402', '0403', '04042', '04081', '04082', '04089', '0410', '04100', '04101', '04102',
'04103', '04104', '04105', '04109', '0411', '04110', '04111', '04112', '04119', '0412',
'0413', '0414', '04141', '04142', '04143', '04149', '0415', '0416', '0417', '0418',
'04181', '04182', '04183', '04184', '04185', '04186', '04189', '0419', '390', '3929',
'7953', '79531', '79539', 'V090', 'V091', 'V092', 'V093', 'V094', 'V0950', 'V0951',
'V096', 'V0970', 'V0971', 'V0980', 'V0981', 'V0990', 'V0991', 'V1204'))   

```



```{r primary diagnosis infection}

c2014$infection <- with(c2014,ifelse ((dx1 %in% inf | dx2 %in% inf), 1,0))

c2014 %>% count(infection) # primary diagnosis
```


```{r arrythmias}
arry <- as.character(c('4270',  '4271','42731','42741', '42742', '4275','4272', '42789', '4279', '7850', '7851')) 

c2014$arry <- with(c2014, ifelse((dx1 %in% arry | dx2 %in% arry), 1, 0)) 

c2014 %>% count(arry)
```

